Concretizing the Process Hitting into Biological Regulatory Networks

### 2013-04-17 parts/infer-ig.tex
Add TODOs and REWRITEs
minor adds
add unsigned edges to IG inference

@@

We are now able to infer the edges of the final IG by considering positive and negative influences
(\pref{pps:inference-IG}).
We infer a positive (resp. negative) edge if there exists a corresponding influence with the same
sign. If an influence is both positive and negative, we infer an unsigned edge. In the end, the
threshold of each edge is the minimum threshold for which the influence has been found. As unsigned
edges represent ambiguous interactions, no threshold is inferred.
\begin{proposition}[Interaction Graph inference]\label{pps:inference-IG}
We infer $\IG = (\Gamma,E_+,E_-,E_\pm)$ from \pref{pps:inference-edges} as follows:
\begin{align*}
E_+ &= \{a \xrightarrow{t} b \mid \nexists a \xrightarrow{t'} b \in \hat{E}_-
  \wedge t = \min \{ l \mid a \xrightarrow{l} b \in \hat{E}_+\}\} \\
E_- &= \{a \xrightarrow{t} b \mid \nexists a \xrightarrow{t'} b \in \hat{E}_+
  \wedge t = \min \{l \mid a \xrightarrow{l} b \in \hat{E}_-\}\} \\
E_\pm &= \{a \rightarrow b \mid \exists a \xrightarrow{t} b \in \hat{E}_+ \wedge \exists a \xrightarrow{t'} b \in \hat{E}_-\} \\
\end{align*}
\end{proposition}

>>>>

%\todo{Try to use projections in order to perform the IG inference}

@@

We are now able to infer the edges of the final IG by considering positive and negative influences
(\pref{pps:inference-IG}).
We infer a positive (resp. negative) edge if there exists a corresponding influence with the same
sign. If an influence is both positive and negative, we infer an unsigned edge. In the end, the
threshold of each edge is the minimum threshold for which the influence has been found. As unsigned
edges represent ambiguous interactions, no threshold is inferred.
\begin{proposition}[Interaction Graph inference]\label{pps:inference-IG}
We infer $\IG = (\Gamma,E)$ from \pref{pps:inference-edges} as follows:
\begin{align*}
E_+ &= \{ \GRNedge{a}{+}{t}{b} \mid \nexists a \xrightarrow{t'} b \in \hat{E}_-
  \wedge t = \min \{ l \mid a \xrightarrow{l} b \in \hat{E}_+\}\} \\
E_- &= \{ \GRNedge{a}{-}{t}{b} \mid \nexists a \xrightarrow{t'} b \in \hat{E}_+
  \wedge t = \min \{l \mid a \xrightarrow{l} b \in \hat{E}_-\}\} \\
E_\pm &= \{ \GRNedge{a}{\uns}{t}{b} \mid \exists a \xrightarrow{t'} b \in \hat{E}_+ \wedge \exists a \xrightarrow{t''} b \in \hat{E}_-
  \wedge t = \min \{l \mid a \xrightarrow{l} b \in \hat{E}_- \cup \hat{E}_+\}\} \\
\end{align*}
\end{proposition}
